---
output:
  html_document:
    css: ['styles.css', 'shared-styles.css']
---
<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
## `r fetchReportMetadataField(data,'title')` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r fetchReportMetadataField(data,'stationId')` - `r fetchReportMetadataField(data,'stationName')`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'primaryParameter'))) {paste("**Primary Time Series:**",  fetchReportMetadataField(data,'primaryParameter'))}`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'referenceParameter'))) {paste("**Reference Time Series:**",  fetchReportMetadataField(data,'referenceParameter'))}`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'upchainParameter'))) {paste("**Upchain Time Series:**",  fetchReportMetadataField(data,'upchainParameter'))}`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'comparisonSeries'))) {paste("**Comparison Time Series:**",  fetchReportMetadataField(data,'comparisonSeries'))}`
</div>
<div class="header-col-right">
**Period:**  `r as.Date(fetchReportMetadataField(data,'startDate'))` to `r as.Date(fetchReportMetadataField(data,'endDate'))`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username") }`
</div>
</div>
</div>

***

```{r echo=FALSE, warning=FALSE, message=FALSE, dev='svg', results='asis'}
Sys.setenv(TZ=data$reportMetadata$timezone)

plots.tables.ALL <- uvhydrographPlot(data)

months_vec <- seq(as.Date(data[['reportMetadata']][['startDate']]), 
                  as.Date(data[['reportMetadata']][['endDate']]), 
                  by="month")
months_nm <- format(months_vec, "%b %Y")

noData_vec <- c()

### Check if there is no data and make noData_vec true if so. 
if(length(plots.tables.ALL) == 0){
  noData_vec <- c(noData_vec, TRUE)
}

for (i in seq_len(length(plots.tables.ALL))) {
  x <- plots.tables.ALL[[i]]
  if(!is.null(x$plot1)){
    noData_vec <- c(noData_vec, FALSE)
    printReportFeature(x$plot1)
    printReportFeature(x$table1, isTable=TRUE)
    printReportFeature(x$ratingShiftTable, isTable=TRUE)
    printReportFeature(x$status_msg1, m=months_nm[i])
    printReportFeature(x$plot2)
    printReportFeature(x$table2, isTable=TRUE)
    printReportFeature(x$status_msg2, m=months_nm[i])
  } else {
    noData_vec <- c(noData_vec, TRUE)
  }
}


noData_msg <- paste("No data for:", paste(months_nm[which(noData_vec)], collapse=", "))

Sys.setenv(TZ="UTC")
```

#`r if(all(noData_vec)){paste("The dataset requested is empty.")}`#

#`r if(!all(noData_vec) & any(noData_vec)){paste(noData_msg)}`#

`r getSimsUrl(data[["simsUrl"]])`

`r printVersionStrings()`