
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```

## `r data[['title']]`  

**Location:**  `r getReportMetadata(data,'stationId')` - `r getReportMetadata(data,'stationName')`

**Period:**  `r as.Date(getReportMetadata(data,'startDate'))` to `r as.Date(getReportMetadata(data,'endDate'))`

**Primary Time Series:** `r getReportMetadata(data,'primaryParameter')`

**Secondary Time Series:** `r getReportMetadata(data,'secondaryParameter')`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`

`r if (length(author) == 0) { paste("**Author:** Username") }`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

***

```{r echo=FALSE, warning=FALSE, message=FALSE, dev='svg', results='asis'}
Sys.setenv(TZ=data$reportMetadata$timezone)

plots.tables.ALL <- uvhydrographPlot(data)

noData_vec <- c()
for (i in seq_len(length(plots.tables.ALL))) {
  x <- plots.tables.ALL[[i]]
  if(!is.null(x$plot1)){
    noData_vec <- c(noData_vec, FALSE)
    par(mar=c(8, 3, 4, 3))
    print(x$plot1)
    cat("\n\n")
    print(kable(x$table1))
    cat("\n\n")
    print(kable(x$status_msg1))
    cat("\n\n")
    print(x$plot2)
    cat("\n\n")
    print(kable(x$table2))
    cat("\n\n")
    print(kable(x$status_msg2))
    cat("\n\n")
  } else {
    noData_vec <- c(noData_vec, TRUE)
  }
}

months_vec <- seq(as.Date(data[['reportMetadata']][['startDate']]), 
                  as.Date(data[['reportMetadata']][['endDate']]), 
                  by="month")
months_nm <- format(months_vec, "%Y-%m")
noData_msg <- paste("No data for:", paste(months_nm[which(noData_vec)], collapse=", "))

Sys.setenv(TZ="UTC")
```

#`r if(all(noData_vec)){paste("The dataset requested is empty.")}`#

#`r if(!all(noData_vec) & any(noData_vec)){paste(noData_msg)}`#

`r getSimsUrl(data)`
