---
output:
  html_document:
    includes:
      before_body: before.html
      after_body: after.html
    css: ['styles.css', 'shared-styles.css']
---

<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
## `r fetchReportMetadataField(reportObject,'title')` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r fetchReportMetadataField(reportObject,'stationId')` `r fetchReportMetadataField(reportObject,'stationName')`

**Time Series:** `r fetchReportMetadataField(reportObject,'timeseriesLabel')`
</div>
<div class="header-col-right">
**Period:**  `r as.Date(fetchReportMetadataField(reportObject,'startDate'))` to `r as.Date(fetchReportMetadataField(reportObject,'endDate'))`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username")}`
</div>
</div>
</div>

***
   
```{r,echo=FALSE,comment=NA,warning=FALSE,results='asis'}
tbl <- sensorreadingTable(reportObject)
library(htmlTable)

if(!identical(tbl, "The dataset requested is empty.")){
  if(isNullOrFalse(reportObject[['reportMetadata']][['excludeComments']])){
    rowColoring <- c("none", "none", "#F7F7F7", "#F7F7F7")
  } else {
    rowColoring <- c("none", "#F7F7F7")
  }
  
   htmlTable(tbl$toRet, 
    cgroup=c("Field Visit Information","Reference Readings","Recorder Readings","Correction Information","Nearest IV"),
    n.cgroup=c(4,4,4,4,3),
    col.rgroup = rowColoring, 
    css.class = "table-cell",
    align="|rrrr|cccc|cccc|rrrr|rrr|",
    rnames=FALSE)
}

```

***

```{r,echo=FALSE,result='asis',comment=NA,warning=FALSE}
if(!identical(tbl, "The dataset requested is empty.")){
  tbl2 <- srsQualifiersTable(reportObject, tbl)
  if(!is.null(tbl2) && nrow(tbl2) > 0){
    if(!is.null(tbl2) && nrow(tbl2) > 0){
      kable(tbl2, align='l', row.names=FALSE, caption = "Qualifiers")
    }
  }
}
```

#`r if(identical(tbl, "The dataset requested is empty.")) {paste(tbl)}`#