---
output:
  html_document:
    css: ['styles.css', 'shared-styles.css']
---
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```

## `r getReportMetadata(data,'title',required=TRUE)` Report

<div class="header">
<div class="header-col-left">
**Location:**  `r getReportMetadata(data,'stationId',required=TRUE)` `r getReportMetadata(data,'stationName')`

`r if(!isEmptyOrBlank(getReportMetadata(data,'primaryLabel'))) {paste("**Primary Series:**", getReportMetadata(data,'primaryLabel'))}`

`r if(!isEmptyOrBlank(getReportMetadata(data,'upchainLabel'))) {paste("**Upchain Series:**", getReportMetadata(data,'upchainLabel'))}`

`r if(!isEmptyOrBlank(getReportMetadata(data,'dvLabel'))) {paste("**Daily Value Series:**", getReportMetadata(data,'dvLabel'))}`
</div>
<div class="header-col-right">
**Period** `r getReportMetadata(data, 'startDate')` to `r getReportMetadata(data, 'endDate')`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username")}`
</div>
</div>

***
   
```{r,echo=FALSE,result='asis',comment=NA,warning=FALSE}
tbl <- extremesTable(data)
# formTable <- padTable(tbl)
# cat(formTable)
if(!identical(tbl, "The dataset requested is empty.")){
  kable(tbl, align='r', row.names=FALSE)
}
```

***

&nbsp;

```{r,echo=FALSE,result='asis',comment=NA,warning=FALSE}
if(!identical(tbl, "The dataset requested is empty.")){
  tbl2 <- extremesQualifiersTable(data, tbl)
  if(!is.null(tbl2) && nrow(tbl2) > 0){
    kable(tbl2, align='l', row.names=FALSE, caption = "Qualifiers")
  }
}
```
`r if(identical(tbl, "The dataset requested is empty.")) {paste(tbl)}`