---
output:
  html_document:
    css: ['styles.css', 'shared-styles.css']
---
<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
## `r fetchReportMetadataField(data,'title')` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r fetchReportMetadataField(data,'stationId')` `r fetchReportMetadataField(data,'stationName')`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'primaryLabel'))) {paste("**Primary Series:**", fetchReportMetadataField(data,'primaryLabel'))}`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'upchainLabel'))) {paste("**Upchain Series:**", fetchReportMetadataField(data,'upchainLabel'))}`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'dvLabel'))) {paste("**Daily Value Series:**", fetchReportMetadataField(data,'dvLabel'))}`
</div>
<div class="header-col-right">
**Period:**  `r as.Date(fetchReportMetadataField(data,'startDate'))` to `r as.Date(fetchReportMetadataField(data,'endDate'))`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username")}`
</div>
</div>
</div>

***
   
```{r,echo=FALSE,result='asis',comment=NA,warning=FALSE}
tbl <- extremesTable(data)
# formTable <- padTable(tbl)
# cat(formTable)
if(!identical(tbl, "The dataset requested is empty.")){
  kable(tbl$toRet, align='r', row.names=FALSE)
}
```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
if(!identical(tbl, "The dataset requested is empty.")){
  if(any(grepl("\\s\\*$", tbl$toRet[,"Date"])) && ncol(tbl$toRet) > 4){cat("*\\* Multiple occurrences of the same extreme on this date. First occurrence listed.*", "\n", seperator="\n")}
  else if(any(grepl("\\s\\*$", tbl$toRet[,"Date"]))){cat("*\\* Multiple occurrences of the same extreme in selected dataset. First occurrence listed.*", "\n", seperator="\n")}

  if(any(grepl("\\s\\*\\*$", tbl$toRet[,"Date"]))){cat("*\\*\\* Multiple occurrences of the same extreme in selected dataset. First occurrence listed.*", "\n", seperator="\n")}
}
```

`r if(identical(tbl, "The dataset requested is empty.")) {paste(tbl)}`

`r if(!identical(tbl, "The dataset requested is empty.")){ if(!isEmptyOrBlank(tbl$footnote)) { tbl$footnote }}`

&nbsp;

***

&nbsp;
```{r,echo=FALSE,result='asis',comment=NA,warning=FALSE}
if(!identical(tbl, "The dataset requested is empty.")){
  tbl2 <- extremesQualifiersTable(data, tbl$toRet, getExtremesConstants()$PRIMARY_HEADER_PREFIX, getExtremesConstants()$UPCHAIN_HEADER_PREFIX)
  if(!is.null(tbl2) && nrow(tbl2) > 0){
    kable(tbl2, align='l', row.names=FALSE, caption = "Qualifiers")
  }
}
```

