```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```

## `r getReportMetadata(data,'title',required=TRUE)` Report

**Location:**  `r getReportMetadata(data,'locationNumber',required=TRUE)` `r getReportMetadata(data,'locationName',required=TRUE)`
   
**Period** `r getReportMetadata(data, 'startDate')` to `r getReportMetadata(data, 'endDate')`

**Primary Series:** `r getReportMetadata(data,'primaryLabel')`

**Upchain Series:** `r getReportMetadata(data,'upchainLabel')`

**Daily Value Series:** `r getReportMetadata(data,'dvLabel')`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`

`r if (length(author) == 0) { paste("**Author:** Username")}`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

***
   
```{r,echo=FALSE,result='asis',comment=NA,warning=FALSE}
tbl <- extremesTable(data)
# formTable <- padTable(tbl)
# cat(formTable)
if(!identical(tbl, "The dataset requested is empty.")){
  kable(tbl, align='r', row.names=FALSE)
}
```
#`r if(identical(tbl, "The dataset requested is empty.")) {paste(tbl)}`#