---
output: pdf_document
---

```{r, echo=FALSE,result='hide',message=FALSE}
library('repgen')
file <- system.file('extdata','06899500_2012_TS.json',package = 'repgen')
ts <- json(file)
```
U.S. DEPARTMENT OF THE INTERIOR - U.S. GEOLOGICAL SURVEY - WATER RESOURCES  
STATION:`r getStr(ts,'locationNumber')` `r getStr(ts,'locationName')` TYPE:`r getStr(ts,'locationType',upper=TRUE)` AGENCY:`r getStr(ts,'locationAgency',TRUE)` STATE:`r getStr(ts,'locationState',TRUE)` COUNTY:`r getStr(ts,'locationCounty')`  
LATITUDE: `r getNum(ts,'locationLat',dec=2)` LONGITUDE: `r getNum(ts,'locationLon',2)` `r getStr(ts,'locationDatum')` DRAINAGE AREA:`r getNum(ts,'locationDrainArea')`  
CONTRIBUTING DRAINAGE AREA:`r getNum(ts,'locationContDrainArea')` DATUM:{missing field}
 Date Processed: `r getDate(ts,'processedTimestamp','%m/%d/%Y')` By swreview  
   
 INPUT DD: Gage height FROM THE DCP (ft)
   
 PROVISIONAL DATA FOR PERIOD `r waterYear(ts,'%m/%d/%Y')`
   
 MAXIMUM FOR PERIOD, BASED ON 365 EQUIVALENT DAYS OF RECORD.  
   
```{r,echo=FALSE,result='asis',comment=NA}
tbl <- extremesTable(ts)
formTable <- padTable(tbl)
cat(formTable)
```

