```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
    isUvHydroReport <- !isEmptyOrBlank(getReportMetadata(data,'title')) && grepl(toupper(getReportMetadata(data,'title')), "UV HYDROGRAPH")
    isCorrReport <- !isEmptyOrBlank(getReportMetadata(data,'title')) && grepl(toupper(getReportMetadata(data,'title')), "CORRECTIONS AT A GLANCE")
    isDvHydroReport <- !isEmptyOrBlank(getReportMetadata(data,'title')) && grepl(toupper(getReportMetadata(data,'title')), "DV HYDROGRAPH")
    isVdiagramReport <- !isEmptyOrBlank(getReportMetadata(data,'title')) && grepl(toupper(getReportMetadata(data,'title')), "V-DIAGRAM")
    isSRSReport <- !isEmptyOrBlank(getReportMetadata(data,'title')) && grepl(toupper(getReportMetadata(data,'title')), "SENSOR READING SUMMARY")
    isSVPReport <- !isEmptyOrBlank(getReportMetadata(data,'title')) && grepl(toupper(getReportMetadata(data,'title')), "SITE VISIT PEAK")
    isExtremesReport <- !isEmptyOrBlank(getReportMetadata(data,'title')) && grepl(toupper(getReportMetadata(data,'title')), "EXTREMES")
    isFiveYrReport <- !isEmptyOrBlank(getReportMetadata(data,'title')) && grepl(toupper(getReportMetadata(data,'title')), "FIVE YEAR GW SUMMARY")
```

<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
`r if(!isEmptyOrBlank(getReportMetadata(data,'title',required=TRUE))) {paste("##",getReportMetadata(data,'title',required=TRUE), "Report")}`
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r getReportMetadata(data,'stationId')` - `r getReportMetadata(data,'stationName')`

<!-- UV Hydrograph / Corr TS --> 
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

```
`r if(!isEmptyOrBlank(getReportMetadata(data,'primaryParameter'))) {paste("**Primary Time Series:**",  getReportMetadata(data,'primaryParameter'))}`

`r if(!isEmptyOrBlank(getReportMetadata(data,'upchainParameter'))) {paste("**Upchain Time Series:**",  getReportMetadata(data,'upchainParameter'))}`

`r if(!isEmptyOrBlank(getReportMetadata(data,'referenceParameter'))) {paste("**Reference Time Series:**",  getReportMetadata(data,'referenceParameter'))}`

<!-- DV Hydrograph / FiveYearGWSum TS -->
`r if(!isEmptyOrBlank(data[['reportMetadata']][['primaryDescriptions']])) {paste("**Primary Time Series:**", data[['reportMetadata']][['primaryDescriptions']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['downChainDescriptions1']])) {paste("**First Down Chain Time Series:**", data[['reportMetadata']][['downChainDescriptions1']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['downChainDescriptions2']])) {paste("**Second Down Chain Time Series:**", data[['reportMetadata']][['downChainDescriptions2']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['downChainDescriptions3']])) {paste("**Third Down Chain Time Series:**", data[['reportMetadata']][['downChainDescriptions3']])}`

<!-- Vdiagram TS ** Currently excluded from using the shared header due to parameter naming conflicts with other reports.-->
<!-- `r if(!isEmptyOrBlank(data[['reportMetadata']][['ratingModelIdentifier']])) {paste("**Time Series:**", data[['reportMetadata']][['ratingModelIdentifier']])}` -->

<!-- Extremes TS -->
`r if(!isEmptyOrBlank(getReportMetadata(data,'primaryLabel'))) {paste("**Primary Series:**", getReportMetadata(data,'primaryLabel'))}`

`r if(!isEmptyOrBlank(getReportMetadata(data,'upchainLabel'))) {paste("**Upchain Series:**", getReportMetadata(data,'upchainLabel'))}`

`r if(!isEmptyOrBlank(getReportMetadata(data,'dvLabel'))) {paste("**Daily Value Series:**", getReportMetadata(data,'dvLabel'))}`

<!-- SiteVisitPeak / SensorReadingSummary TS -->
`r if(!isEmptyOrBlank(getReportMetadata(data,'timeseriesLabel'))) {paste("**Time Series:**", getReportMetadata(data,'timeseriesLabel'))}`

</div>
<div class="header-col-right">
**Period:**  `r as.Date(getReportMetadata(data,'startDate'))` to `r as.Date(getReportMetadata(data,'endDate'))`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username") }`
</div>
</div>
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
excludeZeroNegative <- getReportMetadata(data,'excludeZeroNegative')
```
`r if(!isEmptyOrBlank(excludeZeroNegative) && excludeZeroNegative) {paste("*If zero/negative values are excluded, line will connect non-zero/positive values.*")}`
</div>
