```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
    isUvHydroReport <- !isEmptyOrBlank(fetchReportMetadataField(data,'title')) && grepl(toupper(fetchReportMetadataField(data,'title')), "UV HYDROGRAPH")
    isCorrReport <- !isEmptyOrBlank(fetchReportMetadataField(data,'title')) && grepl(toupper(fetchReportMetadataField(data,'title')), "CORRECTIONS AT A GLANCE")
    isDvHydroReport <- !isEmptyOrBlank(fetchReportMetadataField(data,'title')) && grepl(toupper(fetchReportMetadataField(data,'title')), "DV HYDROGRAPH")
    isVdiagramReport <- !isEmptyOrBlank(fetchReportMetadataField(data,'title')) && grepl(toupper(fetchReportMetadataField(data,'title')), "V-DIAGRAM")
    isSRSReport <- !isEmptyOrBlank(fetchReportMetadataField(data,'title')) && grepl(toupper(fetchReportMetadataField(data,'title')), "SENSOR READING SUMMARY")
    isSVPReport <- !isEmptyOrBlank(fetchReportMetadataField(data,'title')) && grepl(toupper(fetchReportMetadataField(data,'title')), "SITE VISIT PEAK")
    isExtremesReport <- !isEmptyOrBlank(fetchReportMetadataField(data,'title')) && grepl(toupper(fetchReportMetadataField(data,'title')), "EXTREMES")
    isFiveYrReport <- !isEmptyOrBlank(fetchReportMetadataField(data,'title')) && grepl(toupper(fetchReportMetadataField(data,'title')), "FIVE YEAR GW SUMMARY")
```

<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'title'))) {paste("##",fetchReportMetadataField(data,'title'), "Report")}`
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r fetchReportMetadataField(data,'stationId')` - `r fetchReportMetadataField(data,'stationName')`

<!-- UV Hydrograph / Corr TS --> 
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
    if(isUvHydroReport || isCorrReport){
        if(!isEmptyOrBlank(fetchReportMetadataField(data,'primaryParameter'))) {cat("**Primary Time Series:**",  fetchReportMetadataField(data,'primaryParameter'), "\n", sep="\n")}
        if(!isEmptyOrBlank(fetchReportMetadataField(data,'upchainParameter'))) {cat("**Upchain Time Series:**",  fetchReportMetadataField(data,'upchainParameter'), "\n", sep="\n")}
        if(!isEmptyOrBlank(fetchReportMetadataField(data,'referenceParameter'))) {cat("**Reference Time Series:**",  fetchReportMetadataField(data,'referenceParameter'), "\n", sep="\n")}
    } else if(isDvHydroReport || isFiveYrReport){
        if(!isEmptyOrBlank(data[['reportMetadata']][['primaryDescriptions']])) {cat("**Primary Time Series:**", data[['reportMetadata']][['primaryDescriptions']], "\n", sep="\n")}
        if(!isEmptyOrBlank(data[['reportMetadata']][['downChainDescriptions1']])) {cat("**First Down Chain Time Series:**", data[['reportMetadata']][['downChainDescriptions1']], "\n", sep="\n")}
        if(!isEmptyOrBlank(data[['reportMetadata']][['downChainDescriptions2']])) {cat("**Second Down Chain Time Series:**", data[['reportMetadata']][['downChainDescriptions2']], "\n", sep="\n")}
        if(!isEmptyOrBlank(data[['reportMetadata']][['downChainDescriptions3']])) {cat("**Third Down Chain Time Series:**", data[['reportMetadata']][['downChainDescriptions3']], "\n", sep="\n")}
    } else if(isVdiagramReport){
        #NOTE: Vdiagram does not currently actually use this shared header because it renders differently and was unable to access the file
        if(!isEmptyOrBlank(data[['reportMetadata']][['ratingModelIdentifier']])) {cat("**Time Series:**", data[['reportMetadata']][['ratingModelIdentifier']])}
    } else if(isExtremesReport){
        if(!isEmptyOrBlank(fetchReportMetadataField(data,'primaryLabel'))) {cat("**Primary Series:**", fetchReportMetadataField(data,'primaryLabel'), "\n", sep="\n")}
        if(!isEmptyOrBlank(fetchReportMetadataField(data,'upchainLabel'))) {cat("**Upchain Series:**", fetchReportMetadataField(data,'upchainLabel'), "\n", sep="\n")}
        if(!isEmptyOrBlank(fetchReportMetadataField(data,'dvLabel'))) {cat("**Daily Value Series:**", fetchReportMetadataField(data,'dvLabel'), "\n", sep="\n")}
    } else if(isSVPReport || isSRSReport){
        if(!isEmptyOrBlank(fetchReportMetadataField(data,'timeseriesLabel'))) {cat("**Time Series:**", fetchReportMetadataField(data,'timeseriesLabel'))}
    }
```
</div>
<div class="header-col-right">
**Period:**  `r as.Date(fetchReportMetadataField(data,'startDate'))` to `r as.Date(fetchReportMetadataField(data,'endDate'))`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username") }`
</div>
</div>
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
excludeZeroNegative <- fetchReportMetadataField(data,'excludeZeroNegative')
```
`r if(!isEmptyOrBlank(excludeZeroNegative) && excludeZeroNegative) {paste("*If zero/negative values are excluded, line will connect non-zero/positive values.*")}`
</div>
