---
output:
  html_document:
    fig_width: 6
    fig_height: 4
    css: ['shared-styles.css']
---
<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
## `r fetchReportMetadataField(data,'title')` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r data[['reportMetadata']][['stationId']]` - `r data[['reportMetadata']][['stationName']]`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['primarySeriesLabel']])) {paste("**Selected Time Series:**", data[['reportMetadata']][['primarySeriesLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['firstStatDerivedLabel']])) {paste("**Stat Derived Time Series 1:**", data[['reportMetadata']][['firstStatDerivedLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['secondStatDerivedLabel']])) {paste("**Stat Derived Time Series 2:**", data[['reportMetadata']][['secondStatDerivedLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['thirdStatDerivedLabel']])) {paste("**Stat Derived Time Series 3:**", data[['reportMetadata']][['thirdStatDerivedLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['fourthStatDerivedLabel']])) {paste("**Stat Derived Time Series 4:**", data[['reportMetadata']][['fourthStatDerivedLabel']])}`

</div>
<div class="header-col-right">
**Period:**  `r as.Date(data[['reportMetadata']][['startDate']])` to `r as.Date(data[['reportMetadata']][['endDate']])`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username") }`
</div>
</div>
</div>

`r if(!isEmptyOrBlank(fetchReportMetadataField(data, 'excludeDiscrete')) || !isEmptyOrBlank(fetchReportMetadataField(data, 'excludeMinMax'))) {paste("**Advanced Options:**") }` `r if(fetchReportMetadataField(data, 'excludeMinMax')){ paste("Max/min instantaneous values excluded from plot.") }` `r if(!isEmptyOrBlank(fetchReportMetadataField(data, 'excludeDiscrete'))) { paste("Discrete data excluded.") }`


***

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', dev='svg', fig.width=10, fig.height=7}
plot5yr <- createfiveyeargwsumPlot(data)
if (!is.null(plot5yr)) {
  print(plot5yr)
}
```

#`r if(is.null(plot5yr)) {paste("The dataset requested is empty.")}`#

`r getSimsUrl(data[["simsUrl"]])`

`r getWaterDataUrl(data[["waterdataUrl"]])`

`r printVersionStrings()`
