---
output:
  html_document:
    fig_width: 6
    fig_height: 4
---

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```

## `r data[['title']]`  

**Location:**  `r data[['reportMetadata']][['stationId']]` - `r data[['reportMetadata']][['stationName']]`

**Period:**  `r as.Date(data[['reportMetadata']][['startDate']])` to `r as.Date(data[['reportMetadata']][['endDate']])`

**Primary Time Series:** `r data[['reportMetadata']][['primaryDescriptions']]`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`

`r if (length(author) == 0) { paste("**Author:** Username") }`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

***

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', dev='svg', fig.width=10, fig.height=7}
plot5yr <- createfiveyeargwsumPlot(data)
if(!is.null(plot5yr)){
  print(plot5yr)
}
```

#`r if(is.null(plot5yr)) {paste("The dataset requested is empty.")}`#

`r getSimsUrl(data)`

`r getWaterDataUrl(data)`
