---
output:
  html_document:
    css: ['shared-styles.css']
---
<script>document.title="DV Hydro - " + `r fetchReportMetadataField(data,'stationId')`</script>
<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
## `r fetchReportMetadataField(data,'title')` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r fetchReportMetadataField(data,'stationId')` - `r fetchReportMetadataField(data,'stationName')`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['primarySeriesLabel']])) {paste("**Selected Time Series:**", data[['reportMetadata']][['primarySeriesLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['firstStatDerivedLabel']])) {paste("**Stat Derived Time Series 1:**", data[['reportMetadata']][['firstStatDerivedLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['secondStatDerivedLabel']])) {paste("**Stat Derived Time Series 2:**", data[['reportMetadata']][['secondStatDerivedLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['thirdStatDerivedLabel']])) {paste("**Stat Derived Time Series 3:**", data[['reportMetadata']][['thirdStatDerivedLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['fourthStatDerivedLabel']])) {paste("**Stat Derived Time Series 4:**", data[['reportMetadata']][['fourthStatDerivedLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['comparisonSeriesLabel']])) {paste("**Comparison Time Series:**", data[['reportMetadata']][['comparisonSeriesLabel']])}`
</div>
<div class="header-col-right">
**Period:**  `r as.Date(data[['reportMetadata']][['startDate']])` to `r as.Date(data[['reportMetadata']][['endDate']])`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['firstReferenceTimeSeriesLabel']])) {paste("**Reference Time Series 1:**", data[['reportMetadata']][['firstReferenceTimeSeriesLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['secondReferenceTimeSeriesLabel']])) {paste("**Reference Time Series 2:**", data[['reportMetadata']][['secondReferenceTimeSeriesLabel']])}`

`r if(!isEmptyOrBlank(data[['reportMetadata']][['thirdReferenceTimeSeriesLabel']])) {paste("**Reference Time Series 3:**", data[['reportMetadata']][['thirdReferenceTimeSeriesLabel']])}`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username") }`
</div>
<div class="header">
`r if(fetchReportMetadataField(data, 'excludeZeroNegative') || fetchReportMetadataField(data, 'excludeMinMax') || fetchReportMetadataField(data, 'excludeDiscrete')) {paste("**Advanced Options:**") }` 
`r if(fetchReportMetadataField(data, 'excludeZeroNegative')){ paste("Zero/negative values excluded.") }` 
`r if(fetchReportMetadataField(data, 'excludeMinMax')){ paste("Max/min instantaneous values excluded from plot.") }` 
`r if(fetchReportMetadataField(data, 'excludeDiscrete')){ paste("Discrete data excluded.") }`
</div>
</div>

***

```{r echo=FALSE, warning=FALSE, message=FALSE, dev='svg', fig.height=10, fig.width=13, results='hide'}
par(mar=c(13, 4.5, 4, 2))
dvhplot <- createDVHydrographPlot(data)

if(!is.null(dvhplot)){
  secRefPlot <- createDVHydrographRefPlot(data, "firstReferenceTimeSeries", "firstReferenceTimeSeriesLabel")
  terRefPlot <- createDVHydrographRefPlot(data, "secondReferenceTimeSeries", "secondReferenceTimeSeriesLabel")
  quaRefPlot <- createDVHydrographRefPlot(data, "thirdReferenceTimeSeries", "thirdReferenceTimeSeriesLabel")
  printReportFeature(dvhplot)
  printReportFeature(secRefPlot)
  printReportFeature(terRefPlot)
  printReportFeature(quaRefPlot)
}
```

#`r if(is.null(dvhplot)) {paste("The dataset requested is empty.")}`#

`r getSimsUrl(data[["simsUrl"]])`

`r getWaterDataUrl(data[["waterdataUrl"]])`

`r printVersionStrings()`
