
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```

## `r data[['title']]`  

**Location:**  `r data[['reportMetadata']][['stationId']]` - `r data[['reportMetadata']][['stationName']]`

**Period:**  `r as.Date(data[['reportMetadata']][['startDate']])` to `r as.Date(data[['reportMetadata']][['endDate']])`

**First Down Chain Time Series:** `r data[['reportMetadata']][['downChainDescriptions1']]`

**Second Down Chain Time Series:** `r data[['reportMetadata']][['downChainDescriptions2']]`

**Third Down Chain Time Series:** `r data[['reportMetadata']][['downChainDescriptions3']]`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`

`r if (length(author) == 0) { paste("**Author:** Username") }`

**Created:**  `r Sys.time()`

***

```{r echo=FALSE, warning=FALSE, message=FALSE, dev='svg', fig.height=10, fig.width=13, results='hide'}
par(mar=c(13, 3, 4, 2))
dvhplot <- createDvhydrographPlot(data)

if(!is.null(dvhplot)){
  secRefPlot <- createRefPlot(data, "secondary")
  terRefPlot <- createRefPlot(data, "tertiary")
  quaRefPlot <- createRefPlot(data, "quaternary")
  print(dvhplot)
  print(secRefPlot)
  print(terRefPlot)
  print(quaRefPlot)
}
```

#`r if(is.null(dvhplot)) {paste("The dataset requested is empty.")}`#

`r data[['simsUrl']]`

`r data[['waterdataUrl']]`
