---
output:
  html_document:
    includes:
      before_body: before.html
      after_body: after.html
    css: ['styles.css', 'shared-styles.css']
---
<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
##`r fetchReportMetadataField(data,'title')` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r fetchReportMetadataField(data,'stationId')` `r fetchReportMetadataField(data,'stationName')`

**Time Series:** `r fetchReportMetadataField(data,'timeseriesLabel')`
</div>
<div class="header-col-right">
**Period:**  `r as.Date(fetchReportMetadataField(data,'startDate'))` to `r as.Date(fetchReportMetadataField(data,'endDate'))`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username")}`
</div>
</div>

&nbsp;

'*' = Associated Highest Instantaneous Value and Date information will always be blank for the first visit in this report.

`r if(containsOutsideUncertainty(readFieldVisitReadings(data)$diffPeak)){
  paste("'**' = Corrected value is outside of the peak verification reading accounting for uncertainties, and the difference is >0.05 feet. If this is the annual peak, input the peak stage reading into the corrected time series. See SW Memo 2014.06: http://water.usgs.gov/admin/memo/SW/sw14.06_revised.html")}`
</div>

***

```{r,echo=FALSE,comment=NA,warning=FALSE,results='asis'}
tbl <- sitevisitpeakTable(readFieldVisitReadings(data),fetchReportMetadataField(data,'excludeComments'))
library(htmlTable)

if(!identical(tbl, "The dataset requested is empty.")){
  if(isNullOrFalse(fetchReportMetadataField(data,'excludeComments'))){
    groupConfig <- c(4,6,5)
    groupAlign <- "|rrrr|rrrrrr|rrrrr|"
  } else {
    groupConfig <- c(4,5,5)
    groupAlign <- "|rrrr|rrrrr|rrrrr|"
  }
  
  htmlTable(tbl, 
    cgroup=c("Field Visit Information","Peak Verification Information","*Associated Highest Instantaneous Value and Date"),
    n.cgroup=groupConfig,
    col.rgroup = c("none", "#F7F7F7"), css.cell = "padding-left: 1em; padding-right: 1em; padding-top:.5em;padding-bottom:.5em;",
    align=groupAlign,
    rnames=FALSE)
}

```

***

```{r,echo=FALSE,result='asis',comment=NA,warning=FALSE}
if(!identical(tbl, "The dataset requested is empty.")){
  tbl2 <- formatQualifiersTable(readAllFieldVisitQualifiers(readFieldVisitReadings(data)))
  if(!isEmptyOrBlank(tbl2)){
    kable(tbl2, align='l', row.names=FALSE, caption = "Qualifiers")
  }
}
```

#`r if(identical(tbl, "The dataset requested is empty.")) {paste(tbl)}`#
