---
output:
  html_document:
    includes:
      before_body: before.html
      after_body: after.html
    css: styles.css
---

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```

**`r getReportMetadata(data,'title',required=TRUE)` Report**

**Location:**  `r getReportMetadata(data,'stationId',required=TRUE)` `r getReportMetadata(data,'stationName')`

**Period:** `r getReportMetadata(data, 'startDate')` to `r getReportMetadata(data, 'endDate')`

**Time Series:** `r getReportMetadata(data,'timeseriesLabel')`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`

`r if (length(author) == 0) { paste("**Author:** Username")}`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

***

'*' = Associated Highest Instantaneous Value and Date information will always be blank for the first visit in this report.

`r if(containsOutsideUncertainty(data)){
  paste("'**' = Corrected value is outside of the peak verification reading accounting for uncertainties, and the difference is >0.05 feet. If this is the annual peak, input the peak stage reading into the corrected time series. See SW Memo 2014.06: http://water.usgs.gov/admin/memo/SW/sw14.06_revised.html")}`

```{r,echo=FALSE,comment=NA,warning=FALSE,results='asis'}
tbl <- sitevisitpeakTable(data)
library(pander)
library(htmlTable)

if(!identical(tbl, "The dataset requested is empty.")){
  if (output=='pdf') {
    pander(tbl, split.cell = 30, split.table = Inf) 
  } else {
      htmlTable(tbl, 
                  cgroup=c("Field Visit Information","Peak Verification Information","*Associated Highest Instantaneous Value and Date"),
                  n.cgroup=c(4,6,5),
                  #n.cgroup=c(4,6,6), #for spacers  
                  col.rgroup = c("none", "#F7F7F7"), css.cell = "padding-left: 1em; padding-right: 1em; padding-top:.5em;padding-bottom:.5em;",
                  #align.header = paste(rep("c", ncol(tbl)), collapse = ""),
                  align="|rrrr|rrrrrr|rrrrr|",
                  rnames=FALSE)
  }
}

```

***

```{r,echo=FALSE,result='asis',comment=NA,warning=FALSE}
if(!identical(tbl, "The dataset requested is empty.")){
  tbl2 <- svpQualifiersTable(data, tbl)
  htmlTable(tbl2,
              cgroup=c("Qualifiers"),
              n.cgroup=c(3),
              align="|lll|", 
              rnames=FALSE, 
              col.rgroup = c("none", "#F7F7F7"), css.cell = "padding-left: 1em; padding-right: 1em; padding-top:.5em;padding-bottom:.5em;")
}
```

#`r if(identical(tbl, "The dataset requested is empty.")) {paste(tbl)}`#
