---
title: "Corrections at a glance"
output:
  html_document:
    includes:
      before_body: before.html
      after_body: after.html
    css: ['styles.css', 'shared-styles.css']
---
<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
## `r fetchReportMetadataField(data,'title')` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r fetchReportMetadataField(data,'stationId')` - `r fetchReportMetadataField(data,'stationName')`

**Selected Time Series:** `r fetchReportMetadataField(data,'primaryParameter')`
</div>
<div class="header-col-right">
**Period:**  `r as.Date(fetchReportMetadataField(data,'startDate'))` to `r as.Date(fetchReportMetadataField(data,'endDate'))`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username") }`
</div>
</div>
</div>

`r if(!isEmptyOrBlank(fetchReportMetadataField(data, 'excludeCorrections'))){ paste("**Advanced Options: ** Delete region corrections excluded.") }`

***

```{r echo=FALSE, warning=FALSE, message=FALSE, dev='svg', fig.width=18, fig.height=8, results='asis'}
table_timeline <- correctionsataglanceReport(data)
print(table_timeline$timeline)

kable(table_timeline$tableOfLabels, align='l')
```

`r printVersionStrings()`
