---
output:
  html_document:
    includes:
      before_body: before.html
      after_body: after.html
    css: styles.css
  pdf_document:
    includes:
      classoption: legalpaper, landscape
---
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```

## `r data[['reportMetadata']][['title']]`  

**Location:**  `r getReportMetadata(data,'stationId')` - `r getReportMetadata(data,'stationName')`

**Period:**  `r as.Date(getReportMetadata(data,'startDate'))` to `r as.Date(getReportMetadata(data,'endDate'))`

**Primary Time Series:** `r getReportMetadata(data,'primaryParameter')`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`

`r if (length(author) == 0) { paste("**Author:** Username") }`

**Created:**  `r Sys.time()`

***

```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis', dev='svg', fig.width=18, fig.height=9}
par(bty='n', mar=c(5,4,5,2))
table_timeline <- correctionsataglanceReport(data)

table_timeline$timeline

kable(table_timeline$tableOfLabels, align='l')
```

