---
output:
  html_document:
    css: ['shared-styles.css']
---
<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
##  `r data[['reportMetadata']][['title']]` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r data[['reportMetadata']][['stationId']]` - `r data[['reportMetadata']][['stationName']]`

**Time Series:** `r data[['reportMetadata']][['ratingModelIdentifier']]`
</div>
<div class="header-col-right">

**Period:**  `r as.Date(data[['reportMetadata']][['startDate']])` to `r as.Date(data[['reportMetadata']][['endDate']])`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username")}`
</div>
</div>
</div>

***
`r paste("\n  Measurements with a control condition of Anchor, Cover, or Shore Ice are excluded.\n")`
```{r,echo=FALSE,warning=FALSE,fig.height=11,fig.width=10, results='hide', dev='svg'}
renderVDiagram(data)
```
`r paste("\n  Horizontal red bars at max and min gage height for the period shown.\n")`
  
`r paste(historyMeasurementsLabel(data))`
```{r,echo=FALSE,warning=FALSE,fig.height=6,fig.width=7}
vdiagramTable(data, output)
```
