---
output:
  html_document:
    css: ['styles.css','shared-styles.css']
---
<div class="header">
<div>
<div class="header-logo">
```{r echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
cat(getLogo())
```
</div>
<div class="header-title">
## `r fetchReportMetadataField(data,'title')` Report
</div>
</div>
<div class="header-labels">
<div class="header-col-left">
**Location:**  `r fetchReportMetadataField(data,'stationId')` - `r fetchReportMetadataField(data,'stationName')`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'primaryTimeseriesIdentifier'))) {paste("**Selected Time Series:**",  fetchReportMetadataField(data,'primaryTimeseriesIdentifier'))}`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'upchainTimeseriesIdentifier'))) {paste("**Upchain Time Series:**",  fetchReportMetadataField(data,'upchainTimeseriesIdentifier'))}`

`r if(!isEmptyOrBlank(fetchReportMetadataField(data,'ratingModelIdentifier'))) {paste("**Rating Model:**",  fetchReportMetadataField(data,'ratingModelIdentifier'))}`
</div>
<div class="header-col-right">

**Period:**  `r as.Date(fetchReportMetadataField(data,'startDate'))` to `r as.Date(fetchReportMetadataField(data,'endDate'))`

**Created:**  `r sprintf("%s  (%s)", Sys.time(), Sys.timezone())`

`r if (length(author) != 0) { paste("**Author:**",author[[1]]) }`
`r if (length(author) == 0) { paste("**Author:** Username")}`
</div>
</div>
</div>

```{r,echo=FALSE,warning=FALSE,fig.height=11,fig.width=10, results='hide', dev='svg'}
  vplot <- renderVDiagram(data)
```
***
`r ifelse(!is.null(vplot), excludedConditionsMessage(data), "")`
```{r,echo=FALSE,warning=FALSE,fig.height=11,fig.width=10, results='hide', dev='svg'}
  print(vplot)
```

`r ifelse(!is.null(vplot), paste("\n  Horizontal red bars at max and min gage height for the period shown.\n"), "")`
  
`r ifelse(!is.null(vplot) && !isEmptyOrBlank(historyMeasurementsLabel(data)), paste(historyMeasurementsLabel(data)), "")`

```{r,echo=FALSE,warning=FALSE,fig.height=6,fig.width=7}
  if(!is.null(vplot)){
    vdiagramTable(data)
  }
```

#`r if(is.null(vplot)) {paste("The dataset requested is empty.")}`#

`r printVersionStrings()`
